Article data analysis

### 2018-10-15 notebooks/article_notebook.Rmd
updated figures

## Total combinations
```{r}
acquired_report %>%
  left_join(mut_quant[c("gyrA","gyrB","parC","parE","id")], by = "id") %>%
  left_join(mut_report[c("marR","id")], by = "id") %>%
  left_join(isolate_data[c("id", "species")]) %>%
  select(-id) %>%
  group_by_all() %>%
  summarise(n = n()) %>%
  rowwise() %>%
  mutate(Total = 285,
         Percent = round(n/Total * 100,1),
         lwr = round(get_binCI(n, Total)[1], 1),
         upr = round(get_binCI(n, Total)[2], 1),
         "95 % CI" = paste("[", lwr, "-", upr, "]")) %>%
  select(-c(lwr, upr, Total)) %>%
  arrange(desc(n))
```

@@

## Total resistance mechanisms per animal species
```{r}
AddCol <- function(df, col_name) {
  # split rows by delimeters
  string_to_proc <- df %>% select(!!col_name) %>%
    unlist() %>% str_split(regex("\\, |\\,")) 
  # find unique entries
  unique_strings <- string_to_proc %>%
    unlist() %>% unique()
  # construct names of the new columns
  cols_names <- paste(col_name, unique_strings, sep = "_")
  # construct 0/1-content columns for each unique entry
  cols_content <- sapply(function(i) {
    as.integer(unlist(lapply(function(Z) any(Z %in% unique_strings[i]), 
                             X = string_to_proc)))
  }, X = seq_along(unique_strings))
  res <- data.frame(cols_content)
  names(res) <- cols_names
  return(res)
}

@@

ggplot(total_df2, aes(reorder(gene, type), factor(CIP), fill = perc))+
  geom_tile(color = "grey70")+
  annotate("rect", xmin = 0, xmax = 6.5, ymin = -0.5, ymax = 0.2, fill = "grey95", color = "black")+
  annotate("rect", xmin = 6.5, xmax = 12.5, ymin = -0.5, ymax = 0.2, fill = "grey95", color = "black")+
  annotate("rect", xmin = 12.5, xmax = 19.5, ymin = -0.5, ymax = 0.2, fill = "grey95", color = "black")+
  annotate("text", x = 3.25, y = -0.05, label = "gyrA", size = 2.5)+
  annotate("text", x = 9.5, y = -0.05, label = "parC", size = 2.5)+
  annotate("text", x = 16, y = -0.05, label = "parE", size = 2.5)+
  scale_fill_viridis(option = "A",
                     begin = 0.1,
                     guide = guide_colorbar(ticks = F,
                                            barheight = 0.5,
                                            barwidth = 10))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3, size = 8),
        axis.text.y = element_text(size = 8),
        axis.title = element_blank(),
        legend.title = element_blank(),
        legend.position="bottom",
        legend.justification="center",
        legend.direction="horizontal",
        legend.text = element_text(size = 8),
        strip.background = element_rect(colour = "black", fill = "grey70"),
        strip.text = element_text(size = 10))+
  facet_wrap(~species)+
  coord_fixed()
```

>>>>

## Significant differences between resistance mechanisms for each animal species
```{r, warning = F, message = F}
AddCol <- function(df, col_name) {
  # split rows by delimeters
  string_to_proc <- df %>% select(!!col_name) %>%
    unlist() %>% str_split(regex("\\, |\\,")) 
  # find unique entries
  unique_strings <- string_to_proc %>%
    unlist() %>% unique()
  # construct names of the new columns
  cols_names <- paste(col_name, unique_strings, sep = "_")
  # construct 0/1-content columns for each unique entry
  cols_content <- sapply(function(i) {
    as.integer(unlist(lapply(function(Z) any(Z %in% unique_strings[i]), 
                             X = string_to_proc)))
  }, X = seq_along(unique_strings))
  res <- data.frame(cols_content)
  names(res) <- cols_names
  return(res)
}

do_chisq_test <- function(df) {
  df <- df %>%
    slice(expand.grid(1:length(unique(species)), 1:length(unique(species))) %>% rev %>% 
          filter(Var2 < Var1) %>% t) %>%
    mutate(test = rep(1:(n()/2), each = 2)) %>%
    group_by(test) %>%
    do(data_frame(gene = .$key,
                  test = first(.$test),
                  species1 = first(.$species),
                  species2 = last(.$species),
                  data = list(matrix(c(.$Absent,
                                       .$Present),
                                     ncol = 2)))) %>%
    mutate(chi_test = map(data, chisq.test, correct = FALSE)) %>%
    mutate(p.value = map_dbl(chi_test, "p.value"),
           dupl = duplicated(test)) %>%
    filter(dupl == FALSE) %>%
    select(gene, species1, species2, p.value) %>%
    filter(p.value < 0.05)
  return(df)
}

mechanism_per_species <- total_df %>%
  select(-c(gyrA, gyrB, parC, parE)) %>%
  left_join(cols_to_add, by = "id") %>%
  select(id, species, everything()) %>%
  select(-id) %>%
  gather(key, value, -species) %>%
  group_by_all() %>%
  count() %>%
  ungroup() %>%
  mutate(value = if_else(value == 1, "Present", "Absent")) %>%
  spread(value, n, fill = 0) %>%
  select(key, species, Present, Absent) %>%
  split(f = .$key)

p_values_total <- suppressWarnings(lapply(mechanism_per_species, function(x) do_chisq_test(x))) %>%
  bind_rows()

p_values_total
```

@@

## Total resistance mechanisms per animal species
```{r, warning=F, message=F}
total_df <- acquired_report %>%
  left_join(mut_quant[c("gyrA","gyrB","parC","parE","id")], by = "id") %>%
  left_join(mut_report[c("marR","id")], by = "id") %>%
  left_join(isolate_data[c("id", "species")])

@@

ggplot(total_df2, aes(reorder(gene, type), factor(CIP), fill = perc))+
  geom_tile(color = "grey70")+
  annotate("rect", xmin = 0, xmax = 6.5, ymin = -0.5, ymax = 0.2, fill = "grey95", color = "black")+
  annotate("rect", xmin = 6.5, xmax = 12.5, ymin = -0.5, ymax = 0.2, fill = "grey95", color = "black")+
  annotate("rect", xmin = 12.5, xmax = 19.5, ymin = -0.5, ymax = 0.2, fill = "grey95", color = "black")+
  annotate("text", x = 3.25, y = -0.05, label = "gyrA", size = 2.5)+
  annotate("text", x = 9.5, y = -0.05, label = "parC", size = 2.5)+
  annotate("text", x = 16, y = -0.05, label = "parE", size = 2.5)+
  scale_fill_viridis(option = "A",
                     begin = 0.1,
                     guide = guide_colorbar(ticks = F,
                                            barheight = 0.5,
                                            barwidth = 10))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3, size = 8),
        axis.text.y = element_text(size = 8),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 10),
        legend.title = element_blank(),
        legend.position="bottom",
        legend.justification="center",
        legend.direction="horizontal",
        legend.text = element_text(size = 8),
        strip.background = element_rect(colour = "black", fill = "grey70"),
        strip.text = element_text(size = 10))+
  labs(y = "CIP MIC")+
  facet_wrap(~species)+
  coord_fixed()
```
